Reachability problems for counter automata

### 2020-02-28 Documentation/paper.tex
updated incorrect images in paper

\begin{abstract}
\noindent
Reachability is a known problem that can heavily affect the efficiency of code. It has been proven that reachability is decidable for one counter timed automata and to exploit this, we will create a program which will convert c code into such automata. In case the code conforms to the restrictions, enforced by the need of it being a one counter automata, a reachability test can be performed, but the latter will not be part of this research.
\end{abstract}

@@

\begin{lstlisting}[style=CStyle]
bool is_ten(int a){
	int counter = 10;

	if(counter <= a){
		if(counter < a){
			return false;
		}
		return true;
	}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=\linewidth]{less_than_greater_than}
	\caption{Example of a less than expression and a greater than expression.}
	\label{fig:less_than_greater_than}
\end{figure}

Part of the counter automaton of the is\_ten function can be seen in figure \ref{fig:less_than_greater_than}. This automaton has 3 as the start of the outer if and it has 3.01 and 3.02 as respective if and end nodes. The inner if has 4 as the start node, 4.01 as the start of the if segment, and 4.02 as the end node.

>>>>

\begin{abstract}
\noindent
\noindent
Code reachability is a known problem within computer science. It affects the efficiency and readability of code and is therefore a relevant aspect to analyse.

\noindent
This paper will try to provide a clear overview of a means in which we can convert c code into a counter automaton. It has been proven by Daniel Bundala and Joal Ouaknine that the reachability for these can be determined as long as they are restricted to one counter. It will show the different steps taken in an example set up, with explanations with how it works, and why it works.
\end{abstract}

@@

\begin{lstlisting}[style=CStyle]
bool is_ten(int a){
	int counter = 10;
	if(counter <= a){
		if(counter < a){
			return false;
		}
		return true;
	}
	return false;
}
\end{lstlisting}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=\linewidth]{less_than_greater_than}
	\caption{Example of a less than expression and a greater than expression.}
	\label{fig:less_than_greater_than}
\end{figure}
\newpage
Part of the counter automaton of the is\_ten function can be seen in figure \ref{fig:less_than_greater_than}. This automaton has 3 as the start of the outer if and it has 3.01 and 3.02 as respective if and end nodes. The inner if has 4 as the start node, 4.01 as the start of the if segment, and 4.02 as the end node.
